### 2019-06-09 2-Chapters/Conclusion/conclusion.tex
OMG c'est 00h23 un dimanche soir et je bosse !

Finally in Section~\ref{sec:4:retransmissions}, we presented an extension of our model of LPWA networks based on an ALOHA protocol, slotted both in time and frequency.
% , in which dynamic IoT devices can again use machine learning algorithms, to improve their Packet Loss Ratio (PLR) when accessing the network.
If the priority is the Quality of Service (QoS), for instance with renewable energy capabilities, this second model is more appropriate.
We presented and evaluated several heuristics that try to learn how to transmit and retransmit in a smarter way, by using the \UCB{} algorithm for channel selection for first transmission (first-stage), and different proposals based on \UCB{} for the retransmissions upon collisions (second-stage).
The main novelty of this model is to also learn the most efficient way to retransmit packets upon radio collision, by also using a multi-armed bandit algorithm for this second-stage optimization problem.
%
We showed that incorporating learning for the transmission is needed to achieve optimal performance, with significant gain in terms of successful transmission rate in networks with a large number of devices (up-to $30\%$ in the example network).
Our empirical simulations show that each of our proposed heuristic outperforms a naive random access scheme.
Surprisingly, the main take-away message is that a simple \UCB{} learning approach (that simply retransmits in the same channel), turns out to perform as well as more complicated heuristics.

>>>>

Finally in Section~\ref{sec:4:retransmissions}, we presented an extension of our model of LPWA networks based on an ALOHA protocol, slotted in time and frequency.
% , in which dynamic IoT devices can again use machine learning algorithms, to improve their Packet Loss Ratio (PLR) when accessing the network.
If the priority is the Quality of Service (QoS), for instance with renewable energy capabilities, this second model is more appropriate.
We presented and evaluated several heuristics that try to learn how to transmit and retransmit in a smarter way, by using the \UCB{} algorithm for channel selection for first transmission (first-stage), and different proposals based on \UCB{} for the retransmissions upon collisions (second-stage).
The main novelty of this model is to also learn the most efficient way to retransmit packets upon radio collision, by also using a multi-armed bandit algorithm for this second-stage optimization problem.
%
We showed that incorporating learning for the transmission is needed to achieve optimal performance, with significant gain in terms of successful transmission rate in networks with a large number of devices (up-to $30\%$ in the example network).
Our empirical simulations show that each of our proposed heuristic outperforms a naive random access scheme.
Surprisingly, the main take-away message is that a simple \UCB{} learning approach (that simply retransmits in the same channel), turns out to perform as well as more complicated heuristics.
